Geometric variational problems

### 2020-11-13 NSF2020/Description/newspecificaim3.tex
yny

\subsubsection{Effects of electric fields on the dynamic self-assembly}

>>>>

\subsubsection{Electromechanical effects on the dynamic assembly of amphiphiles \label{subsubsec:em_effects}}
Using flicker spectroscopy of the
shape fluctuations of a giant unilamellar vesicle (GUV), the bending rigidity is determined as a function of lipid 
composition from 0 to 100 mol $\%$ of charged lipids in recent experiments \cite{FaizEtAl2019_SoftMatt}:
Membrane bending rigidity increases with lipid surface charge, while decreases with salt in the bulk due to the screening of the lipid surface charge,
in agreement with several theoretical models \cite{Kralchevsky1996_JCIS,May1996_JChemPhys,LoubetEtAl2013_PRE} that also assumed the quadratic form of the elastic energy
density in the presence of surface charge and/or bulk charge \cite{DuplantierGoldstein1990_PRL,Winterhalter1992_JPC}. 
As the electrostatic interaction is non-local in nature, we expect that the controversy of the HK elastic energy form (see \S~\ref{subsec:specific_aim_1}) 
would be worse in the presence of electrostatic interactions and/or electrokinetics. The PIs will extend the approaches in \S~\ref{subsec:specific_aim_1} to charged lipids to calculate the bending moduli and compare against the experimental results in \cite{FaizEtAl2019_SoftMatt}: We propose to incorporate an explicit surface charge on each particle boundary $P_i$
and compute the electrostatic potential as a functional of particle configuration. Adding the electrostatic forces to the hydrophobic attraction forces between particles to compute the particle assembly dynamics, we can then calculate elastic moduli as outlined in \S~\ref{subsec:specific_aim_1}. Results from these proposed calculations provide another comparison/validation of HAP model against the continuum mechanics.

Once the effects of lipid charges on the moduli are verified the PIs propose to examine how to use 
an external electric field to control the amphiphilic self-assembly in solvent. 
PI YNY has a track record of working on electrohydrodynamics
of an elastic, inextensible membrane using both asymptotic analysis \cite{Nganguia2013_PRE,Young2014_JFM,Young2015_PoF} and numerical simulations \cite{Nganguia2015_CiCP}, and will work with both PI RR and BQ to extend the HAP model to study the electromechanical effects on the assembly of amphiphile.
Results from these proposed research will yield quantitative understanding of how to utilize an electric field to achieve optimal control of assembly of amphiphiles in solvent.
